Transitivity of Subtyping for Intersection Types

### 2020-05-14 papers/LMCS-subtyping-intersections/paper.tex
rename

The BCD intersection type system includes a subsumption rule which
states that a term $M$ in environment $\Gamma$ can be given type $B$
if it has type $A$ and $A$ is a subtype of $B$, written $A \leq B$.
\[
\inference{\Gamma \vdash M : A & A \leq B}
          {\Gamma \vdash M : B}
\]
Figure~\ref{fig:BCD-subtyping} reviews the BCD rules for subtyping.
Note that in the (trans) rule, the type $B$ appears in the premises
but not in the conclusion. Thus, the BCD subtyping judgment does not
enjoy the subformula property.  For many other subtyping systems, it
is straightforward to remove the (trans) rule, modify the other rules,
and then then prove transitivity.  Unfortunately, the $({\to}{\cap})$
rule of the BCD system significantly complicates the situation.

@@

Before moving on, we make note of some basic facts regarding the $<:$
relation and the $\topP{A}$ predicate.

>>>>

The BCD intersection type system includes a subsumption rule which
states that a term $M$ in environment $\Gamma$ can be given type $B$
if it has type $A$ and $A$ is a subtype of $B$, written $A \leq B$.
\[
\inference{\Gamma \vdash M : A & A \leq B}
          {\Gamma \vdash M : B}
\]
Figure~\ref{fig:BCD-subtyping} reviews the BCD rules for subtyping.
Note that in the (trans) rule, the type $B$ appears in the premises
but not in the conclusion. Thus, the BCD subtyping judgment does not
enjoy the subformula property.  For many other subtyping systems, it
is straightforward to remove the (trans) rule, modify the other rules,
and then prove transitivity.  Unfortunately, the $({\to}{\cap})$
rule of the BCD system significantly complicates the situation.

@@

Before moving on, we take note of some basic facts regarding the $<:$
relation and the $\topP{A}$ predicate.
